Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-12-09 WSSSPE3/report/WSSSPE3_review.tex
small fixes in abstract comments

\begin{abstract}
\todo{need to update this abstract for WSSSPE3}
This technical report records and discusses the Third Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE3). 
%The workshop used an
%alternative submission and peer-review process, which led to a set of papers
%divided across five topic areas: 
The report includes a description of keynote presentation and a set of lightning
talks, and focuses on the discussions, future steps, and future organization for
a set of self-organized working groups.
For each group, the report also includes a point of contact and a landing
page that can be used by those who want to join that group's future activities.
\todo{think about if there are more general conclusions we want to highlight from WSSSPE3}
%%
%The workshop recognized that reliance on scientific software
%is pervasive in all areas of world-leading research today. The workshop
%participants then proceeded to explore different perspectives on the concept of
%sustainability. Key enablers and barriers of sustainable scientific software
%were identified from their experiences. In addition,
%recommendations with new requirements such as software credit files and software
%prize frameworks were outlined for improving practices in sustainable software
%engineering.
%%
%There was also broad consensus that formal
%training in software development or engineering was rare among the
%practitioners. Significant strides need to be made in building a sense of
%community via training in software and technical practices, on increasing their
%size and scope, and on better integrating them directly into graduate education
%programs.
%%
%Finally, journals can define and publish policies to improve reproducibility, whereas
%reviewers can insist that authors provide sufficient information and access to
%data and software to allow them reproduce the results in the paper. Hence a list of
%criteria is compiled for  journals to provide to reviewers so as to make it easier to
%review software submitted for publication as a ``Software Paper.''

>>>>

\begin{abstract}
This technical report records and discusses the Third Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE3). 
%The workshop used an
%alternative submission and peer-review process, which led to a set of papers
%divided across five topic areas: 
The report includes a description of keynote presentation and a set of lightning
talks, and focuses on the discussions, future steps, and future organization for
a set of self-organized working groups.
For each group, the report also includes a point of contact and a landing
page that can be used by those who want to join that group's future activities.
\todo{think about if there are any general conclusions we want to highlight from WSSSPE3}
%%
%The workshop recognized that reliance on scientific software
%is pervasive in all areas of world-leading research today. The workshop
%participants then proceeded to explore different perspectives on the concept of
%sustainability. Key enablers and barriers of sustainable scientific software
%were identified from their experiences. In addition,
%recommendations with new requirements such as software credit files and software
%prize frameworks were outlined for improving practices in sustainable software
%engineering.
%%
%There was also broad consensus that formal
%training in software development or engineering was rare among the
%practitioners. Significant strides need to be made in building a sense of
%community via training in software and technical practices, on increasing their
%size and scope, and on better integrating them directly into graduate education
%programs.
%%
%Finally, journals can define and publish policies to improve reproducibility, whereas
%reviewers can insist that authors provide sufficient information and access to
%data and software to allow them reproduce the results in the paper. Hence a list of
%criteria is compiled for  journals to provide to reviewers so as to make it easier to
%review software submitted for publication as a ``Software Paper.''
